### 2018-02-13 Writing/Thesis/content/chapter-approach.tex
table and figure overhaul

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ \hline
		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ \hline
		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ \hline
		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\label{tab:table1}
	\caption{This is a caption text.}
\end{table}

% How is the regression ranking done
One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models. The idea is to use separate regression models to predict a performance value for each classifier, and to then derive an ordering from these predictions. This is done by splitting the data set compiled beforehand into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier. The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus a regression model can be trained on each of them. All regression models therefore try to learn the target function $meta features \rightarrow classifier performance value$ for their respective classifier. Hence for a query instance, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved. In a second step, the classifiers are ordered according to the predictions.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ \hline
		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ \hline
		...				& ...	& ...				& ...					\\ \hline
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ \hline
		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ \hline
		...				& ...	& ...				& ...					\\ \hline
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
	\end{tabularx}

\vspace{1em}
...
\vspace{1em}

	\begin{tabularx}{\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ \hline
		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ \hline
		...				& ...	& ...				& ...					\\ \hline
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
	\end{tabularx}

	\label{tab:table1}
	\caption{This is a caption text.}
\end{table}

% How is the preference ranking done
The second possibility considered in this context is using preference learning to predict a ranking. Each instance of the data set generated beforehand contains meta feature information for the considered data set and performance values of all classifiers. Similarly to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values. This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking. In this case, there exists only one label ranking mode which is fed the computed meta data for a new data set and returns an ordering of classifiers. Thereby it attempts to learn the mapping from meta features to an ordering of classifiers directly.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1				& MF 2				& ... 	& MF n				& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ \hline
		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ \hline
		...				& ...				& ...	& ...				& ...		& ...		&	...	&	...			\\ \hline
		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\label{tab:table1}
	\caption{This is a ranking}
\end{table}

\section{Implementation}

META FEATURES USED!

for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before

>>>>

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ 
		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\label{tab:performanceValues}
	\caption{This is a caption text.}
\end{table}

\subsection{Regression Based Ranking}
% How is the regression ranking done
One possibility to derive a ranking of classifiers from this information when given a new data set is to use regression models. The idea is to use separate regression models to predict a performance value for each classifier, and to then derive an ordering from these predictions. This is done by splitting the data set compiled beforehand into separate data sets that each contain all meta features for all data sets, but only the performance values of one classifier. The target feature on these individual data sets, the performance value of the classifier, is a numeric value, and thus a regression model can be trained on each of them. All regression models therefore try to learn the target function $meta features \rightarrow classifier performance value$ for their respective classifier. Hence for a query instance, after computing the meta features, these are fed into each regression model and the predicted performance value for each classifier is saved. In a second step, the classifiers are ordered according to the predictions.

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
	\end{tabularx}
}	
\vspace{1em}
...
\vspace{1em}	
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
	\end{tabularx}
}
	\label{tab:regressionTables}
	\caption{This is a caption text.}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/regression_models.pdf}
\caption{A model of the regression based ranker}
\label{fig:regression_ranker_model}
\end{figure}

\subsection{Preference Based Ranking}
% How is the preference ranking done
The second possibility considered in this context is using preference learning to predict a ranking. Each instance of the data set generated beforehand contains meta feature information for the considered data set and performance values of all classifiers. Similarly to the regression alternative, the performance values can be converted to preference information by sorting the corresponding classifiers by their performance values. This leads to an ordering of classifiers associated with each instance, and implies that the preference learning task at hand is label ranking. In this case, there exists only one label ranking mode which is fed the computed meta data for a new data set and returns an ordering of classifiers. Thereby it attempts to learn the mapping from meta features to an ordering of classifiers directly.

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1				& MF 2				& ... 	& MF n				& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\
		...				& ...				& ...	& ...				& ...		& ...		&	...	&	...			\\
		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\label{tab:preferenceTable}
	\caption{This is a ranking}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/label_ranking_model.pdf}
\caption{A model of the preference based ranker}
\label{fig:preference_ranker_model}
\end{figure}

\section{Implementation}
% regression based model - weka used

% preference learning
The jPL framework is a java framework for the evaluation of preference learning algorithms. It implements several tasks from the context of preference learning, including label ranking.

% meta features - openML webapp
\cite{OpenML2013}
% Which meta features
As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used. Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew. Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}. Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material. Since the meta data also includes probing, which is generally an expensive operation and furthermore does not aid in proving the point of a connection of properties of a data set and the performance of classifiers, additionally to the full meta features all evaluation measures where computed without using those meta features that use probing.

### 2018-02-13 Writing/Thesis/content/chapter-evaluation.tex
table and figure overhaul

% !TEX root = ../my-thesis.tex
%
\chapter{Evaluation}
\label{sec:evaluation}

@@

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{chapter:fundamentals}. These include the Kendall rank correlation coefficient, loss and best three loss. For all three measures, it is computed if any advantage or disadvantage one solutions has is significant, by means of the Mann-Whitney U and its P-value. The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

@@

% Which meta features
As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used. Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew. Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}. Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material. Since the meta data also includes probing, which is generally an expensive operation and furthermore does not aid in proving the point of a connection of properties of a data set and the performance of classifiers, additionally to the full meta features all evaluation measures where computed without using those meta features that use probing.

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on [MACHINE DETAILS]. [TIMEOUT AND HARDWARE ALLOCATION DETAILS]. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. When a timeout occurred, the predictive accuracy was set to 0.

@@

\input{tables/evaluationResults}
\ref{tab:evaluationResults}

\input{tables/significanceResults}
\ref{tab:significanceResults}

\tikzsetnextfilename{LossGraphics}
\begin{figure}
\pgfplotsset{width=.5\textwidth}
\begin{tikzpicture}
\begin{axis}[ylabel={BestThreeLoss}, xlabel={Data Set}]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}%
~%
%
%\begin{tikzpicture}
%\begin{axis}[ymin=-5, ymax=25,ylabel={BestThreeLoss}, xlabel={Data Set}]
%\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
%\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
%\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
%\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
%\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
%\end{axis}
%\end{tikzpicture}
\caption{The Best Three Loss for the Best Algorithm Baseline and the Random Forest Ranker (Full Meta Data)}
\label{fig:lossGraphics}
\end{figure}

>>>>

\chapter{Evaluation}
\label{sec:evaluation}

@@

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{sec:fundamentals}. These include the Kendall rank correlation coefficient, loss and best three loss. For all three measures, it is computed if any advantage or disadvantage one solutions has is significant, by means of the Mann-Whitney U and its P-value. The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

@@

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on a linux cluster, each node consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 16GB RAM with usage of up to 150 nodes. There was a timeout of eight hours set for the computation of a single performance value of a classifier on a data set. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.

%TODO integrate DONT FORGET META FEAUTRES (WHY EVERYTHING X2??)
for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before analysis
apache commons implementation for Kendall Rank correlation as well
JAICore implementation for stratified split of data set

@@

\input{tables/evaluationResults}

\input{tables/significanceResults}

\tikzsetnextfilename{LossGraphics}
\begin{figure}
%\pgfplotsset{width=\textwidth}
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
	title=regular scale,
	height=\textwidth,
	width=\textwidth,
	ylabel={BestThreeLoss}, 
	xlabel={Data Set},
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}%
~%
%
\begin{tikzpicture}
\begin{axis}[
	title=log scale (base 2),
	height=\textwidth,
	width=\textwidth,
	ylabel={BestThreeLoss}, 
	xlabel={Data Set},
	ymode=log,
	log basis y={2}
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}
}
\caption{The Best Three Loss for the Best Algorithm Baseline and Random Forest Ranker (Full Meta Data)}
\label{fig:lossGraphics}
\end{figure}

### 2018-02-13 Writing/Thesis/content/chapter-fundamentals.tex
more writing
table and figure overhaul

% !TEX root = ../my-thesis.tex
%
\chapter{Fundamentals}
\label{sec:fundamentals}

@@

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\hsize=1.1\hsize}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X  >{\hsize=1.7\hsize}X}
		%\hline
		Feature	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Sepal length}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Sepal width}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Petal length}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Petal width} 	& Species			\\ \hline
				& 5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				& 5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				& 5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				& 5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				& 6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				& 5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				& 7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				& 5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				& 6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\label{tab:iris}
	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context). The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
\end{table}

@@

\begin{table}[h]
\centering
	\begin{tabularx}{.8\textwidth}{>{\hsize=0.9\hsize}X | >{\hsize=.1\hsize}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash} >{\hsize=.1\hsize}X}
		%\hline
		Species		& 	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris virginica}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris versicolor}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris setosa}	& 	\\ \hline
		Label		& [ & 1,									& 2,										& 3 									& ] \\ 
		Score		& [ & 0.17,								& 0.12,									& 0.89 								& ] \\ 
		Ranking		& [ & 2,									& 3,										& 1 									& ] \\ 
		Ordering		& [ & 3,									& 1,										& 2 									& ] \\ 		
	\end{tabularx}
	\label{tab:ranking_vs_ordering}
	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context). The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
\end{table}

@@

\subsection{Meta Learning}
% Context is meta learning -> what does that mean and what are the consequence
Meta leThe previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets. In the context of meta learning, is 'possible to learn about the learning process
itself, and in particular that a system could learn to profit from previous
experience to generate additional knowledge that can simplify the automatic
selection of efficient models summarizing the data' \cite{razdil2008metalearning}.

>>>>

\chapter{Fundamentals}
\label{sec:fundamentals}

@@

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | X}
		%\hline
		\multicolumn{1}{X}{Sepal length}	& \multicolumn{1}{X}{Sepal width}	& \multicolumn{1}{X}{Petal length}	& \multicolumn{1}{X}{Petal width} & Species			\\ \hline
				5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\caption{The information the gardener in the example could have gathered; this is an excerpt from the well known iris data set \cite{iris}}
	\label{tab:iris}
\end{table}

@@

\begin{table}[h]
\centering
	\begin{tabularx}{.8\textwidth}{>{\hsize=0.9\hsize}X | >{\hsize=.1\hsize}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash} >{\hsize=.1\hsize}X}
		%\hline
		Species		& 	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris virginica}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris versicolor}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris setosa}	& 	\\ \hline
		Label		& [ & 1,									& 2,										& 3 									& ] \\ 
		Score		& [ & 0.17,								& 0.12,									& 0.89 								& ] \\ 
		Ranking		& [ & 2,									& 3,										& 1 									& ] \\ 
		Ordering		& [ & 3,									& 1,										& 2 									& ] \\ 		
	\end{tabularx}
	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context). The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
	\label{tab:ranking_vs_ordering}
\end{table}

@@

\subsection{Meta Learning}
% Context is meta learning -> what does that mean and what are the consequence
Meta leThe previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets. In the context of meta learning, is 'possible to learn about the learning process
itself, and in particular that a system could learn to profit from previous
experience to generate additional knowledge that can simplify the automatic
selection of efficient models summarizing the data' \cite{brazdil2008metalearning}.

### 2018-02-13 Writing/Thesis/content/chapter-related-work.tex
more writing + adding some picture
table and figure overhaul

\tikzsetnextfilename{MLPlanTasks}
\begin{figure}
\tikzset{edge from parent/.style={draw,->}}
\begin{tikzpicture}[sibling distance=10em,
  every node/.style = {shape=rectangle, rounded corners,
    draw, align=center}]]
  \node {\textcolor{uniblue}{classify}}
    child { node {...} }
    child { node {\textcolor{uniblue}{classifyWithNN}}
    child { node {...} }
      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
        child { node {...} }
        child { node {...} 
          child { node {...}  }
          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } } } }
    };
\end{tikzpicture}
\caption{An example for how the complex task 'classify' might be broken down by ML-Plan. The figure is loosely adapted from \cite{wever2017automatic}. Nodes containing '...' represent an undefined number of subtrees. \textcolor{uniblue}{Complex tasks} and \textcolor{uniaccentblue}{primitive tasks} are distinguished by their color.}
\label{fig:mltree}
\end{figure}

>>>>

%\tikzsetnextfilename{MLPlanTasks}
\begin{figure}
\centering
%\tikzset{edge from parent/.style={draw,->}}
%\begin{tikzpicture}[sibling distance=10em,
%  every node/.style = {shape=rectangle, rounded corners,
%    draw, align=center}]]
%  \node {\textcolor{uniblue}{classify}}
%    child { node {...} }
%    child { node {\textcolor{uniblue}{classifyWithNN}}
%    child { node {...} }
%      child { node {\textcolor{uniblue}{buildNN} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN}}
%        child { node {...} }
%        child { node {...} 
%          child { node {...}  }
%          child { node {\textcolor{uniaccentblue}{addLayer} \\ ... \\ \textcolor{uniaccentblue}{addLayer} \\ \textcolor{uniaccentblue}{trainNN} \\ \textcolor{uniaccentblue}{predictFromNN} } %} } }
%    };
%\end{tikzpicture}
\includegraphics[width=.8\textwidth]{gfx/MLPlan.pdf}
\caption{An example for how the complex task 'classify' might be broken down by ML-Plan, adapted from \cite{wever2017automatic}. Nodes containing '...' represent an undefined number of subtrees.}
\label{fig:mltree}
\end{figure}
